---
title: "Investigating content and audience reactions to youtube Super Bowl commercials"
author: "by R-Mageddon"
output: github_document
---

```{r load-packages, echo = FALSE, message=FALSE, warning=FALSE}
# load packages here
library(tidyverse)
library(lubridate)
library(ggrepel)
library(viridis)
library(hrbrthemes)
library(scales)
library(RColorBrewer)
library(tm)
library(ggwordcloud)
library(tidytext)
library(syuzhet)
library(stringr)
library(textdata)
library(patchwork)
```

```{r load-data, echo = FALSE, message=FALSE,warning=FALSE}
# load data here
youtube <- readr::read_csv('data/youtube.csv', show_col_types = FALSE) 

```

## Introduction

Our `youtube` dataset contains a list of ads from the 10 brands that had the most
advertisements in Super Bowls from 2000 to 2020, according to data from 
superbowl-ads.com, with matching videos found on YouTube. These brands included 
Toyota, Bud Light, Kia, Coca-Cola, Hynudai, Budweiser, Pepsi, NFL, Doritos, and E-trade.
It was then analyzed by the staff of FiveThirtyEight, an American website that 
focuses on opinion poll analysis, politics, economics, and sports blogging, to 
come up with seven defining characteristics of a Super Bowl ad: `funny`, `danger`, 
`use_sex`, `show_product_quickly`, `celebrity`, `patriotic`, `animals`, which are 
represented as boolean variables. Furthermore, we are also given the `view_count`, 
`like_count`, `dislike_count`,`favorite_count`, `comment_count`, `description`, 
and `title` for each ad. 



## Question 1：What is the trend of the ads' content and audience preferences over the years?

### Introduction
Many things have changed in the first 20 years of the 21st century. There are 
life science breakthroughs, political conflicts, feminist movements, etc. 
Therefore, we want to see if people’s reaction to Super Bowl commercials reflect 
the changes in their lifestyles and thoughts over the years. The changes in the 
ads themselves may also tell how companies are reacting to audience preferences.

We want to explore the trends in how the ads change over the years in terms of 
content, audience preferences, and engagement. To analyze the change in content 
we use the logical variables `funny`,`danger`,`use_sex`,`patriotic`,
`show_product_quickly`, `celebrity`, and `animals`. To explore audience 
preference and engagement,`like_count`, `comment_count`, and `view_count` are 
used to calculate ratio of like/engagement over total views.



### Approach

For the first plot, we used a stacked area chart to see how the attribute makeup
of ads has changed over time. This is achieved by first counting the total number 
of `TRUE`-valued Boolean variable in each year and then determining of the total `TRUE`
values how many come from each attribute. These are then grouped by year and
plotted as a stacked area chart. We preferred this visualization over the 
stacked bar chart with years on the y-axis since the stacked area chart makes it 
easier to identify the change, if any, in the trend of content proportions over 
the years.  

For the second plot, we used a line graphs faceted by `attribute`, a variable 
that is created using all logical variables in the data set. The faceted line
graph is suitable for time-dependent changes by each categorical variable. 
Because the logical variables are either true or false, 2 different lines in 
each sub-plot clearly show how the trends (audience preference in this case) 
differ if an ad contains an attribute or not.



### Analysis
Plot 1: 
```{r counter}
# First, create a function that returns total count of a specific attribute in one year.
count_attribute_number <-
  function(data, attribute_name, desired_year) {
    count1 = 0
    for (i in seq(1, nrow(data))) {
      if (data$year[i] == desired_year) {
        if (data[i, attribute_name] == TRUE) {
          count1 = count1 + 1
        }
      }
    }
    return(count1)
  }
```

```{r generator}
# With help from the counter above, we define a new function that creates a 
## generalized attribute counting dataframe for a single year.
generator <- function(data, year) {
  funny_count = count_attribute_number(data, "funny", year)
  show_quickly_count = count_attribute_number(data, "show_product_quickly", year)
  patriotic_count = count_attribute_number(data, "patriotic", year)
  celebrity_count = count_attribute_number(data, "celebrity", year)
  danger_count = count_attribute_number(data, "danger", year)
  animals_count = count_attribute_number(data, "animals", year)
  use_sex_count = count_attribute_number(data, "use_sex", year)
  
  year_value <- rep(year, 7)
  count_of_attribute <-
    c(
      funny_count,
      show_quickly_count,
      patriotic_count,
      celebrity_count,
      danger_count,
      animals_count,
      use_sex_count
    )
  attributes <- c(
    "Funny",
    "Show product quickly",
    "Patriotic",
    "Celebrity",
    "Danger",
    "Animals",
    "Use sex"
  )
  year_table <- cbind(year_value, count_of_attribute, attributes)
  year_df <- as.data.frame(year_table)
  return(year_df)
}
```

```{r appender}
# Then, using the "appender" function below to get the final dataframe for 
## all years from 2000 to 2020.
appender <- function(data) {
  year_general_df <- generator(data, 2000)
  for (j in seq(2001, 2020)) {
    year_general_df <- rbind(year_general_df,
                             generator(data, j))
  }
  return(year_general_df)
}
```

```{r STACKED-BAR-CHART}
# Use the function and get our desired plot
youtube1 <- youtube
year_attribute_df <- appender(youtube1)
year_attribute <- year_attribute_df %>%
  mutate(
    year_value = as.numeric(as.character(year_value)),
    count_of_attribute = as.numeric(as.character(count_of_attribute))
  ) %>%
  group_by(year_value, attributes) %>%
  summarise(n = sum(count_of_attribute), .groups = "drop_last") %>%
  mutate(percentage = n / sum(n))

# Plot stacked area chart
ggplot(year_attribute,
       aes(x = year_value, y = percentage, fill = attributes)) +
  geom_area(alpha = 0.6 ,
            size = .5,
            colour = "white") +
  scale_y_continuous(
    labels = label_percent(
      accuracy = NULL,
      scale = 100,
      prefix = "",
      suffix = "%",
      big.mark = " ",
      decimal.mark = ".",
      trim = TRUE
    )
  ) +
  labs(
    x = "Year",
    y = "Percentage",
    fill = "Attributes",
    title = "Percentage comparison among video attributes in\nSuperbowl commercials over years (2000~2020)",
    subtitle = "By video attributes"
  ) +
  theme_ipsum() +
  scale_fill_brewer(palette = "Dark2") +
  theme(plot.title = element_text(hjust = 0, size = 13, face = "plain"))
```

Plot 2:
```{r wrangling_function}
# create compare function for different
# Function was written with the help of TA
create_compare <- function(varname, full_data) {
  full_data <- full_data %>%
    # drop N/A value for key variables
    drop_na({
      {
        varname
      }
    }, like_count, view_count, dislike_count, comment_count) %>%
    # create new variables for preference, dislike, engagement, and attributes
    mutate(
      like = like_count / view_count,
      dislike = dislike_count / view_count,
      engage = comment_count / view_count,
      attribute = as_label(enquo(varname))
    ) %>%
    select({
      {
        varname
      }
    }, like, dislike, engage, attribute, year) %>%
    rename(val = as_label(enquo(varname)))
  return(full_data)
}
```


```{r create new table}
# create a new data frame that contains key variables
all_compare <- rbind(
  create_compare(funny, youtube),
  create_compare(danger, youtube),
  create_compare(show_product_quickly, youtube),
  create_compare(patriotic, youtube),
  create_compare(celebrity, youtube),
  create_compare(animals, youtube),
  create_compare(use_sex, youtube)
) %>%
  # change variable names to be more readable
  mutate(
    attribute = recode(
      attribute,
      'animals' = 'Animals',
      'celebrity' = 'Celebrity',
      'danger' = 'Danger',
      'funny' = 'Funny',
      'patriotic' = 'Patriotic',
      'show_product_quickly' = 'Show product quickly',
      'use_sex' = 'Use sexuality'
    )
  ) %>%
  group_by(year, attribute, val) %>%
  summarise(
    mean_like = mean(like),
    mean_engage = mean(engage),
    .groups = "drop"
  )
```


```{r like plot, fig.width = 10}
# plotting like vs. year
ggplot(all_compare, aes(x = as.numeric(year), y = mean_like)) +
  geom_line(aes(color = val)) +
  labs(
    title = "Audience preferences for Youtube Superbowl Commercials\nEach year from 2000 to 2020",
    subtitle = "By video attributes and year",
    x = "Year of Superbowl",
    y = "Average ratio of likes over views"
  ) +
  facet_wrap(~ attribute, nrow = 3) +
  scale_y_continuous(
    labels = label_percent(
      accuracy = NULL,
      scale = 100,
      prefix = "",
      suffix = "%",
      big.mark = " ",
      decimal.mark = ".",
      trim = TRUE
    )
  ) +
  scale_x_continuous(breaks = c(2000, 2004, 2008, 2012, 2016, 2020)) +
  theme_minimal() +
  scale_color_manual("Does the ads contain\n this attribute?", 
                     values = c("#808080", "#FF0000"),
                     labels = c("No", "Yes")) +
  theme(
    axis.title.x = element_text(hjust = 0.5),
    axis.title.y = element_text(margin = margin(r = 20),
                                hjust = 0.5),
    panel.spacing = unit(1.5, "lines"),
    legend.position = c(0.9, 0.1),
    plot.title = element_text(size = 12),
    panel.grid.minor = element_blank()
  ) 

```


### Discussion

Thus, we should focus on the width of each color bands, instead 
of trying to interpret the lines. Here, we can see that over the years, `funny` 
and `show_product_quickly` take up the highest proportion among the seven video 
attributes. However, both of them are showing a decreasing trend when it's around
2020. In fact, other attributes, such as `patriotic` and `use_sex`, experiencing 
decreases recently. And `celebrity` is, nevertheless, having an increasing 
relative proportion. attribute `patriotic` takes up the least proportion overall,
but it reaches its peak proportion around 2017. 

For line plots, we first look at audience preference of various attributes in ads. 
From 2000 to 2020, the ads that contain dangerous elements are getting more likes 
than ads that do not contain dangerous elements. There is no obvious trend that 
the audience strongly prefer a specific attribute other than `danger` over the 
years.In certain years, audience feel strongly about ads that contain specific 
attributes. In 2010, ads that contain `animals` element are liked more than 3 
times compared to ads that do not contain animals. Same observation is shown 
for ads containing `patriotic` element in 2010. However, from 2017 to 2020, 
ads that contain `patriotic` content become less liked. Ads that use sexuality 
are far more liked in 2004 but are less liked in 2015. In 2002, the ads that 
have no humorous element are liked almost 3 times as ads that have humorous 
element. 

Then, we look at what kinds of ads elicit the audience to engage by commenting.
In general, the engagement rate is pretty low. However, in 2004 specifically there 
is are significant differences between engagement rate for all attributes. Ads that
contain `animal`, `funny`, show product quickly, or use sexuality shows higher 
engagement compared the ads that don't contain these attributes. On the other hand, 
ads that don't contain `celebrity`, `patriotic`, or `danger` tend to have higher
engagement rates.

The year variable used here denotes the Superbowl year where the commercial was 
shown. However, some commercials have a different published date on Youtube.
Furthermore, the youtube videos have been collected from random Youtube users 
instead of influencers or official commercial accounts. Therefore, the views, likes,
and engagement also depend on the account itself.



## Question 2 How do election year ads differ from non-election year ads in terms of content and description?


### Introduction

Our second question aims to explore the difference, if any, between ads aired during 
election years compared to those aired during non-election years. Particularly, 
we want to analyze if there is any noticeable difference in the description and 
content between the election and non-election year ads. Answering this question 
involves looking at the `title` variable to analyze how these ads were described, 
and then analyzing the boolean content variables of `use_sex`, `patriotic`,`funny`
,`celebrity`,`danger`, and `animals` to see if they had any noticeable differences
in their content. Finally, the `year` variable is also needed to distinguish between
election and non-election years.

We are interested in exploring this question because election years mark a significant
cultural moment in the US. Therefore, we want to see whether this focus on politics
translates into any noticeable effect on super bowl ads. 

### Approach


To analyze the description aspect of our question, we decided to use a word cloud
visualization since we felt it was the most informative way to visualize what major
descriptors are used for the ads. The alternative way of analyzing `title` that 
we considered included a bar char for top 10-20 words. However, we decided to opt
for the word cloud since it provided more information in terms of relative occurrences
of all the words being used (by size). Creating the word cloud involved cleaning the
text (for e.g turning all words lower, removing punctuation, removing numbers) which
was done by the `tm` library. We also performed sentiment analysis on the words
using the `get_sentiment()` function and colored the word cloud based on the
words' sentiment score. We used the `syuzhet` library for the `get_sentiment` function
since it assigned each word a sentiment score and had the widest range of words that 
could be assigned a score i.e largest word dictionary.

To analyze the content aspect, we decided to opt for a column graph with percentage
values of each content category as labels of the visualization. Possible alternative
that we considered was a pie chart but since our column graph shows the percentage
values as well as count values, we decided to go for the visualziation that 
maximized information. 

### Analysis

``` {r data-prep-election-wordcloud}
# Election years in the dataset
election_year <- c(2000, 2004, 2008, 2012, 2016, 2020)
# Adding an election year variable
youtube <- youtube %>%
  mutate(election_years = ifelse(year %in% election_year, 1, 0))
# Data Wrangling steps
test <- youtube %>%
  filter(election_years == 1) %>%
  select(title)

word_cloud_viz <- function(testvector,freqCheck) {
  docs <- VCorpus(VectorSource(testvector))
  docs <- docs %>%
    # Removing numbers
    tm_map(removeNumbers) %>%
    # Removing punctuation
    tm_map(removePunctuation) %>%
    # Removing whitespace
    tm_map(stripWhitespace)
  docs <- tm_map(docs, content_transformer(tolower))
  docs <- tm_map(docs, removeWords, stopwords("english"))
  # Removing words that contain brand names
  docs <- tm_map(
    docs,
    removeWords,
    c(
      "super",
      "bowl",
      "commercial",
      "superbowl",
      "bud ",
      "light",
      "budweiser",
      "pepsi",
      "hyundai",
      "doritos",
      "coke",
      "cocacola",
      "cola",
      "coca",
      "kia",
      "toyota",
      "etrade",
      "nfl"
    )
  )
  dtm <- TermDocumentMatrix(docs)
  matrix <- as.matrix(dtm)
  words <- sort(rowSums(matrix), decreasing = TRUE)
  election_df <- data.frame(word = names(words), freq = words)
  election_df <- election_df %>%
    mutate(angle = sample(-45:45, nrow(election_df), replace = TRUE)) %>%
      filter(freq >= freqCheck) %>%
    # Package to get sentiment scores for each word in the dataset
    mutate(sentiment = get_sentiment(word, "syuzhet"))
  retPlot <- election_df %>% 
    ggplot(aes(
    label = word,
    color = sentiment,
    size = freq,
    angle = angle
  )) +
  geom_text_wordcloud() +
  theme_minimal() +
  scale_color_gradient(low = "#FFD662FF", high = "#00539CFF")
  return(retPlot)
  
}

```

``` {r election-wordcloud-viz, fig.height = 10}

election_1 <- youtube %>%
  filter(election_years == 1) %>%
  select(title)

election_0 <- youtube %>%
  filter(election_years == 0) %>%
  select(title)

election_wc <- word_cloud_viz(election_1,1)

nelection_wc <- word_cloud_viz(election_0,2)

efinal <- election_wc +
  scale_radius(range = c(2, 15)) +
  labs(
    title = "Election Year Ad Title Word Cloud",
    subtitle = "Colored by Sentiment
      Bluer for postive sentiment
      Brown for neutral sentiment
      Yellower for negative sentiment"
  )

nefinal <- nelection_wc +
  scale_radius(range = c(3.5, 15)) +
  labs(
    title = "Non-election Year Ad Title Word Cloud",
    subtitle = "Colored by Sentiment
      Bluer for postive sentiment
      Brown for neutral sentiment
      Yellower for negative sentiment"
  ) 

efinal / nefinal

```


``` {r election-col-plot}
# Creating variable with election, using pivot_longer to get attributes in the
# same column, and creating a percentage variable
election_yr <- youtube %>%
  pivot_longer(cols = c(use_sex, funny, celebrity, patriotic, danger, animals)) %>%
  filter(election_years == 1) %>%
  filter(value == TRUE) %>%
  group_by(name) %>%
  summarise(n = n()) %>%
  mutate(perc = paste(round((n / sum(
    n
  )) * 100), "%", sep = ""))
# Creating the plot
elecyr <-election_yr %>%
  ggplot(aes(y = name, x = n, fill = name)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = perc, color = name),
            nudge_x = 2,
            show.legend = FALSE) +
  labs(
    x = "Count",
    y = "Ad Attribute",
    title = "Count and Proportion of Ad by Attribute",
    subtitle = "In Election Years"
  ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme_minimal()+
  scale_y_discrete(labels = rev(c("Use Sex",
                              "Patriotic",
                              "Funny",
                              "Danger",
                              "Celebrity",
                              "Animals")))
```




```{r non-election-col-plot, fig.height=5}
# Creating variable with no election, using pivot_longer to get attributes in the
# same column, and creating a percentage variable
no_election_yr <- youtube %>%
  pivot_longer(cols = c(use_sex, funny, celebrity, patriotic, danger, animals)) %>%
  filter(election_years == 0) %>%
  filter(value == TRUE) %>%
  group_by(name) %>%
  summarise(n = n()) %>%
  mutate(perc = paste(round((n / sum(
    n
  )) * 100), "%", sep = ""))
# No Election year col vizualization
nelecyr <- no_election_yr %>%
  ggplot(aes(y = name, x = n, fill = name)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = perc, color = name),
            nudge_x = 4,
            show.legend = FALSE) +
  labs(
    x = "Count",
    y = "Ad Attribute",
    subtitle = "In Non-Election Years"
  ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme_minimal() +
  scale_y_discrete(labels = rev(c("Use Sex",
                              "Patriotic",
                              "Funny",
                              "Danger",
                              "Celebrity",
                              "Animals")))

elecyr / nelecyr
```


### Discussion

We can divide the discussion of our visualizations into two parts: comparison by
description and comparison by content. 

 When comparing our two words clouds, it immediately becomes clear that there is 
 some overlap in the words used in Superbowl Ad titles. These include, winner, 
 new, and nfl. Similarly, there does not seem to be any major difference in the 
 overall sentiment makeup of these words. We can gauge this by observing that both 
 the word clouds have a few blue words (indicating positive sentiment), very few
 yellow words (indicating negative sentiment), and majority brown words 
 (indicating neutral sentiment). This goes on to indicate that there is very 
 little difference in the titles of superbowl ads in election years compared to 
 non-election years. This result was surprising since our team was expecting the
 election titles to contain more patriotic words such as "America", "Freedom", 
 and "Liberty" but it appears as if the ad titles are not significantly affected
 by election and non-election years. 

 We observed a similar relation when analyzing the content of election and 
 non-election year ads. For both these categories, there seemed to be a marginal
 difference in the attribute makeup, indicating that even the content of ads was
 very similar in election and non-election years. However, it was interesting to
 note that `use_sex` attribute dropped from 14% in non-election years to 9% in 
 election years. While this could be indicative of a slight variation in content,
 it more more likely that this change was a coincidence.  


## Presentation

Our presentation can be found [here](presentation/presentation.html).

## Data 

Mock, T 2021, *Superbowl commercials*, electronic dataset, 
tidytuesday, viewed 20 September 2021,
<https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-03-02/readme.md>.

## References

https://www.r-graph-gallery.com/136-stacked-area-chart
https://cran.r-project.org/web/packages/syuzhet/vignettes/syuzhet-vignette.html
https://cran.r-project.org/web/packages/ggwordcloud/vignettes/ggwordcloud.html