---
title: "Project proposal"
author: "R-Megaddon: Yihan Shi, Holly Cui, Raffay Rana"
output: github_document
---

```{r load-packages, message = FALSE, warning=FALSE}
library(tidyverse)
```

```{r load data}
youtube <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-02/youtube.csv', show_col_types = FALSE)
```

## Dataset

The `youtube` dataset contains a list of ads from the 10 brands that had the most advertisements 
in Super Bowls from 2000 to 2020, according to data from superbowl-ads.com, with 
matching videos found on YouTube. It was then analyzed by FiveThirtyEight staffers
to come up with seven defining characteristics of a Super Bowl ad represented as
boolean value columns. These include:
 
`funny`: Did the ad contain humor?

`patriotic`: Did the commercial make a patriotic appeal, either clear or subtle, 
or include American imagery? Any glimpses of an American flag or the words "America" 
or "United States" counted, as did references to the armed forces, manufacturing
and farming.

`celebrity`: Did the ad feature a celebrity?

`danger`: Did the ad contain any violence, threats of violence, injuries, fighting 
or guns? Any allusions to death or hokey injuries also counted here.

`animals`: Did it include animals? Did an animal — either real or computer-generated 
— show up at any point in the ad? Even one-frame appearances counted.

`use_Sex`: Did it use sex to sell its product? We counted any subtle or overt 
suggestions of sex, sexuality, sex appeal or nudity.
 
Other variables in the dataset include the commercial’s brand, title, thumbnail,
description, year, poster channel’s name, Youtube ID, Youtube etag, Youtube URL,
and audience engagement metrics (likes, dislikes, comments, favourites). In total,
the `youtube` dataset has `r dim(youtube)[1]` rows and `r dim(youtube)[2]` columns.


## Motivation

We chose this dataset because Super Bowl commercials are an important cultural 
marker in the US and exploring their content and engagement can potentially reveal some
interesting insights. More specifically, we are interested in digging into the dataset's several 
boolean content variables and how they influence the views and likes of the ads. Then, we also want  
look at how this relation has changed over the years and whether there is 
any trend between certain years and the kinds of ads made in those years. 
Lastly, the variables in the dataset are also clean and convenient to be pulled and used, 
which allows us to delve directly into data visualization and analysis. 

## Questions

1. Are there any trends in how the ads change over the years in terms of content, 
audience preferences and engagement? 

2. How do election year ads differ from non-election year ads in terms of content 
and description?


## Analysis plan

To answer the first question, we will make a time series plot with `year` on the
x-axis and the boolean characteristics on the y-axis. This can either be done by 
creating a binary time series plot and then faceting by characteristics or by 
wrangling the data such that for each year we have a column that has all the 
characteristics of the ad from that year, which can then be used as a label for the plot. 
This will give us an idea of how the characteristic makeup of the ads has changed over time. 
It would then be interesting to look at how the `like_count`, `dislike_count`, and `view_count` 
changed over the years and whether there was any relation between ad 
characteristic and audience engagement. We also intend on creating new
variables such as `like/view` and `dislike/view` to account for different total views 
of the ads over the years. 
 

Answering the second question will involve a series of visualizations. After filtering our
data for just election years, we will create word clouds for ad titles and ad captions
to see if there are any particular words that appear more frequently then others. 
We will complement this by adding a bar graph to show the count of the most prominent
characteristics of these ads. Then, we will repeat the process for non-election years and 
compare our results to note any differences. We also intend on either creating new 
variables or summarizing existing variables to account for the fact that there are more
non-election years than election years in the dataset.

