---
title: "Holly-Plot1"
author: "Holly Cui"
date: "9/29/2021"
output: github_document
---
### Introduction
Introduction to the question and what parts of the dataset are necessary to answer the question. Also discuss why you’re interested in this question.

### Approach 
...We also used a stacked area chart to see how the proportion of each feature change
over the years. A stacked area chart is similarly plotted as a stacked bar plot, but with
lines connecting the elements with same group, which is visually compatible when we plan to 
have year(time variable) as our x axis. More specifically, over the years on the x axis, we 
can see the relative percentage change of each video feature on the y axis with areas divided 
by lines linking them together. The percentage, or proportion, of each feature is calculated
by first counting the total number of TRUE-valued Boolean variable in each year ("funny", 
"patriotic", etc.), and then generate a dataframe with all 21 years together. 


```{r load libraries}
library(tidyverse)
library(lubridate)
library(dplyr)
library(ggrepel)
library(viridis)
library(hrbrthemes)

youtube <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-02/youtube.csv', show_col_types = FALSE)
youtube1 <- youtube
```

### Analysis
```{r STACKED-BAR-CHART}
# First, create a function that returns total count of a specific feature in one year.
count_feature_number <- function(data, feature_name, desired_year){
  count1 = 0
  for (i in seq(1, nrow(data))){
    if (data$year[i] == desired_year){
      if (data[i, feature_name] == TRUE){
        count1 = count1 + 1
      }
    }
  }
  return(count1)
}


# With help from the counter above, we define a new function that creates a 
## generalized feature counting dataframe for a single year.
generator <- function(data, year){
  funny_count = count_feature_number(data, "funny", year) 
  show_quickly_count = count_feature_number(data, "show_product_quickly", year)
  patriotic_count = count_feature_number(data, "patriotic", year)
  celebrity_count = count_feature_number(data, "celebrity", year)
  danger_count = count_feature_number(data, "danger", year)
  animals_count = count_feature_number(data, "animals", year)
  use_sex_count = count_feature_number(data, "use_sex", year)
  
  year_value <- rep(year, 7)
  count_of_feature <- c(funny_count, show_quickly_count, patriotic_count, 
                        celebrity_count, danger_count, animals_count, use_sex_count)
  features <- c("funny", "show_product_quickly", "patriotic", 
                "celebrity", "danger", "animals", "use_sex")
  year_table <- cbind(year_value, count_of_feature, features)
  year_df <- as.data.frame(year_table)
  return(year_df)
}


# Then, using the "appender" function below to get the final dataframe for 
## all years from 2000 to 2020. 
appender <- function(data){
  year_general_df <- generator(data, 2000)
  for (j in seq(2001, 2020)){
    year_general_df <- rbind(year_general_df, 
                             generator(data, j))
  }
  return(year_general_df)
}


# Use the function and get our desired plot
year_feature_df <- appender(youtube1)

year_feature <- year_feature_df %>%
  mutate(
    year_value = as.numeric(as.character(year_value)),
    count_of_feature = as.numeric(as.character(count_of_feature))
  ) %>%
  group_by(year_value, features) %>%
  summarise(n = sum(count_of_feature)) %>%
  mutate(percentage = n / sum(n))

year_feature

# Plot stacked area chart
ggplot(year_feature, aes(x = year_value, y = percentage, fill = features)) + 
    geom_area(alpha=0.6 , size=.5, colour="white") +
    labs(
      x = "Year", 
      y = "Percentage", 
      fill = "Features",
      title = "Percentage comparison among video features in\nSuperbowl commercials over years (2000~2020)",
      subtitle = "By video features"
    ) + 
    theme_ipsum() +
    theme(
      plot.title = element_text(hjust = 0, size = 13)
    )
  


```


```{r TIME-SERIES-PLOT}
# wrangle data grouped by year
youtube2 <- youtube1 %>%
  drop_na(year, view_count, like_count, dislike_count) %>%
  group_by(year) %>%
  summarise(sum_view = sum(view_count), sum_like = sum(like_count), sum_dislike = sum(dislike_count))
youtube2

# ratio: `like/view` and `dislike/view`
youtube3 <- youtube2 %>%
  mutate(
    like_view_rate = sum_like/sum_view, 
    dislike_view_rate = sum_dislike/sum_view
  )
youtube3

# Initial thought: a pure geom_line plot with view-count vs. year
ggplot(youtube3, aes(x = year, y = sum_view)) +
  geom_line() + 
  labs(
    title = "sum_view"
  )
# However, from the plot, we saw point for 2012 has extremely higher value than points for other years. 
# This reminds us to take like_count and dislike_count into account and average on the total view count to see if the "outlier" can be balanced. 

# Plot ratio plot
ggplot(youtube3, aes(x = year)) +
  geom_line(aes(y = like_view_rate)) +
  labs(
    title = "like/view ratio"
  )
ggplot(youtube3, aes(x = year)) +
  geom_line(aes(y = dislike_view_rate), color = "red") +
  labs(
    title = "dislike/view ratio"
  )
# From the two lines (the reason why they are not put on the same plot is because of different scale of y axis), 
# we can see the outlier has been balanced. The pattern is different, which should be taken into account. 

# The final plot: 
ggplot(data = youtube3, aes(x = year, y = sum_view)) +
  geom_line(aes(size = like_view_rate), color = "blue") +
  stat_smooth(
  color = "red", fill = "grey",
  linetype = "dashed",
  method = "loess"
  ) +
  labs(
    y = "Total number of view",
    title = "Total number of view of Superbowl commercials over years",
    subtitle = "with like/view rate as weight on size",
    size = "like / view"
  )
# The final plot takes into account three different aspects: the sum_view over years, sum of like count averaged on total view count, and the regression smoothed line with confidence interval. 

```




```{r PIE-CHART}
# Find the total number of TRUE values in each Boolean variable
funny_true_count = length(youtube1$funny[youtube1$funny == TRUE])
showproduct_true_count = length(youtube1$show_product_quickly[youtube1$show_product_quickly == TRUE])
patriotic_true_count = length(youtube1$patriotic[youtube1$patriotic == TRUE])
celebrity_true_count = length(youtube1$celebrity[youtube1$celebrity == TRUE])
danger_true_count = length(youtube1$danger[youtube1$danger == TRUE])
animals_true_count = length(youtube1$animals[youtube1$animals == TRUE])
use_sex_true_count = length(youtube1$use_sex[youtube1$use_sex == TRUE])
# Make a new dataframe based on the elements
youtube_pie_df <- tibble(
  category = c("Funny", "Show product quickly", "Patriotic", "Celebrity", "Danger", "Animals", "Use sex"),
  count = c(funny_true_count, showproduct_true_count, patriotic_true_count, celebrity_true_count, 
            danger_true_count, animals_true_count, use_sex_true_count)
)
# Compute the position of labels on the pie chart
youtube_pie_df <- youtube_pie_df %>% 
  arrange(desc(category)) %>%
  mutate(
    ypos = cumsum(count)- 0.5*count, 
    perc = count / sum(count) * 100, 
    percentage = paste0(round(perc, digits = 1), "%") 
    # create new variable regarding the proportion that each element takes up among total
    ) 

# Plot the chart
ggplot(youtube_pie_df, aes(x="", y=count, fill=category)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() +
  geom_text(aes(y = ypos, label = percentage), color = "black", size=3.5) +
  scale_fill_brewer(palette="Pastel2") +
  labs(
    title = "Count of use of the elements included in\nSuperbowl Commercials", 
    fill = "Element include"
  ) +
  theme(
   plot.title = element_text(face = "bold", size = 12, hjust = 0.5)
  )
```

### Discussion
In the stacked area plot, we should focus on the width of each color bands, instead
of trying to interpret the lines. Here, we can see that over the years, `funny` and 
`show_product_quickly` take up the highest proportion among the seven video features.































