---
title: "Investigating content and audience reactions to youtube Super Bowl commercials"
subtitle: "(2000 to 2020)"
author: "R_mageddon <br> Yihan Shi, Holly, Cui, Raffay Rana"
institute: "Duke University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
# Remove any packages from this list that you're not using
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(wordcloud)
library(RColorBrewer)
library(tm)
library(wordcloud2)
library(ggwordcloud)
library(tidytext)
library(syuzhet)
library(stringr)
library(textdata)
library(hrbrthemes)
library(scales)
```

```{r setup, include = FALSE}
# For better figure resolution
knitr::opts_chunk$set(
  fig.retina = 3, 
  dpi = 300, 
  fig.width = 6, 
  fig.asp = 0.618, 
  out.width = "70%"
  )
```

```{r load-data, include = FALSE}
youtube <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-02/youtube.csv', 
                           show_col_types = FALSE)
```

```{r style-slides, echo = FALSE}
style_xaringan(
  title_slide_background_image = "img/watercolour_sys02_img34_teacup-ocean.jpg"
)
```


## Introduction

- Many things have changed in the first 20 years of the 21st century, such as 
life science breakthroughs, political conflicts, feminist movements, etc.

- Could the characteristics of Super Bowl commercials give us some insights about
such changes?

---

## What feature make the audience wants to hit 'like' for an ad?

```{r wrangling_function, echo = FALSE, warning = FALSE, message=FALSE}
# create compare function for different categories
create_compare <- function(varname, full_data) {
  full_data <- full_data %>% 
    # drop N/A value for key variables 
    drop_na({{varname}}, like_count, view_count, dislike_count, comment_count) %>% 
    # create new variables for preference, dislike, engagement, and features
    mutate(like = like_count / view_count,
           dislike = dislike_count / view_count,
           engage = comment_count / view_count,
           feature = as_label(enquo(varname))) %>% 
    select({{varname}}, like, dislike, engage, feature, year) %>%
    rename(val = as_label(enquo(varname)))
  return(full_data)
}

# create a new data frame that contains key variables from above 
all_compare <- rbind(create_compare(funny, youtube),
                     create_compare(danger, youtube),
                     create_compare(show_product_quickly, youtube),
                     create_compare(patriotic, youtube),
                     create_compare(celebrity, youtube),
                     create_compare(animals, youtube),
                     create_compare(use_sex, youtube)) %>% 
  # change variable names to be more readable
  mutate(feature = recode(feature, 'animals' = 'Animals', 
                          'celebrity' = 'Celebrity', 
                          'danger' = 'Danger',
                          'funny' = 'Funny',
                          'patriotic' = 'Patriotic',
                          'show_product_quickly' = 'Show product quickly',
                          'use_sex' = 'Use sexuality')) %>% 
  group_by(year, feature, val) %>% 
  summarise(mean_like = mean(like),
            mean_engage = mean(engage))
```


```{r plot-compare, warning = FALSE, out.width = "70%", fig.width = 8, echo = FALSE, message=FALSE}
# Code hidden with echo = FALSE
# Uses modified penguins dataset from previous chunk
# Play around with height and width until you're happy with the look

ggplot(all_compare, aes(x = as.numeric(year), y = mean_like)) + 
  geom_line(aes(color = val)) + 
  labs(title = "Audience preferences for Youtube Superbowl Commercials\nEach year from 2000 to 2020",
       subtitle = "By video features and year",
       x = "Year of Superbowl",
       y = "Average ratio of likes over views") +
  facet_wrap(~feature) +
  scale_color_manual("Feature", values = c("#808080", "#FF0000")) +
  scale_y_continuous(labels = label_percent(accuracy = NULL, scale = 100, prefix = "",
                                            suffix = "%", big.mark = " ", decimal.mark = ".", trim = TRUE)) +
  scale_x_discrete(limits=c(2000,2004,2008,2012,2016,2020)) + 
  theme_minimal() +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(margin = margin(r = 20),
                                    hjust = 0.5),
        panel.spacing = unit(1.5, "lines"),
        legend.position = c(0.95, 0.1),
        legend.title = element_blank())
```

---

## Any trends in how the ads change over the years in terms of content?

```{r STACKED-BAR-CHART, echo = FALSE, warning = FALSE, message=FALSE}

# First, create a function that returns total count of a specific feature in one year.
count_feature_number <- function(data, feature_name, desired_year){
  count1 = 0
  for (i in seq(1, nrow(data))){
    if (data$year[i] == desired_year){
      if (data[i, feature_name] == TRUE){
        count1 = count1 + 1
      }
    }
  }
  return(count1)
}


# With help from the counter above, we define a new function that creates a 
## generalized feature counting dataframe for a single year.
generator <- function(data, year){
  funny_count = count_feature_number(data, "funny", year) 
  show_quickly_count = count_feature_number(data, "show_product_quickly", year)
  patriotic_count = count_feature_number(data, "patriotic", year)
  celebrity_count = count_feature_number(data, "celebrity", year)
  danger_count = count_feature_number(data, "danger", year)
  animals_count = count_feature_number(data, "animals", year)
  use_sex_count = count_feature_number(data, "use_sex", year)
  
  year_value <- rep(year, 7)
  count_of_feature <- c(funny_count, show_quickly_count, patriotic_count, 
                        celebrity_count, danger_count, animals_count, use_sex_count)
  features <- c("Funny", "Show product quickly", "Patriotic", 
                "Celebrity", "Danger", "Animals", "Use sex")
  year_table <- cbind(year_value, count_of_feature, features)
  year_df <- as.data.frame(year_table)
  return(year_df)
}


# Then, using the "appender" function below to get the final dataframe for 
## all years from 2000 to 2020. 
appender <- function(data){
  year_general_df <- generator(data, 2000)
  for (j in seq(2001, 2020)){
    year_general_df <- rbind(year_general_df, 
                             generator(data, j))
  }
  return(year_general_df)
}


# Use the function and get our desired plot
year_feature_df <- appender(youtube)

year_feature <- year_feature_df %>%
  mutate(
    year_value = as.numeric(as.character(year_value)),
    count_of_feature = as.numeric(as.character(count_of_feature))
  ) %>%
  group_by(year_value, features) %>%
  summarise(n = sum(count_of_feature)) %>%
  mutate(percentage = n / sum(n))
```


```{r plotting stacked area chart, warning = FALSE, out.width = "60%", fig.height = 5, fig.width = 7, echo = FALSE}
# Plot stacked area chart
ggplot(year_feature, aes(x = year_value, y = percentage, fill = features)) + 
    geom_area(alpha=0.6 , size=.5, colour="white") +
    scale_y_continuous(labels = label_percent(accuracy = NULL, scale = 100, 
                                              prefix = "", suffix = "%", 
                                              big.mark = " ", 
                                              decimal.mark = ".", 
                                              trim = TRUE)) +
    labs(
      x = "Year", 
      y = "Percentage", 
      fill = "Features",
      title = "Percentage comparison among video features in\nSuperbowl commercials over years (2000~2020)",
      subtitle = "By video features"
    ) + 
    theme_ipsum() +
    scale_fill_brewer(palette = "Dark2") +
    theme(
      plot.title = element_text(hjust = 0, size = 13)
    )
```

---


.center[
``` {r data-prep-election-wordcloud, echo = FALSE, warning = FALSE}
# # Election years in the dataset
election_year <- c(2000, 2004, 2008, 2012, 2016, 2020)
# Adding an election year variable
youtube <- youtube %>%
  mutate(election_years = ifelse(year %in% election_year, 1, 0))

test <- youtube %>%
  filter(election_years == 1) %>%
  select(title)

docs <- VCorpus(VectorSource(test))
docs <- docs %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, c(
  "super", "bowl", "commercial", "superbowl",
  "bud", "light", "budweiser", "pepsi",
  "hyundai", "doritos", "coke", "cocacola",
  "cola", "coca", "kia", "toyota"
))
dtm <- TermDocumentMatrix(docs)
matrix <- as.matrix(dtm)
words <- sort(rowSums(matrix), decreasing = TRUE)
election_df <- data.frame(word = names(words), freq = words)


election_df <- election_df %>%
  mutate(angle = sample(-45:45, nrow(election_df), replace = TRUE)) %>%
   # Package to get sentiment scores for each word in the dataset
  mutate(sentiment = get_sentiment(word,"syuzhet"))
```

``` {r election-wordcloud-viz, warning = FALSE, out.width = "90%", fig.width = 10, fig.height = 11, echo = FALSE}
elec_word_C <-election_df %>%
  ggplot(aes(
    label = word,
    color = sentiment,
    size = freq,
    angle = angle
  )) +
  geom_text_wordcloud() +
  scale_radius(range = c(2, 15)) +
  theme_minimal() +
  scale_color_gradient(low = "#FFD662FF", high = "#00539CFF") +
  labs(
    title = "Election Year Ad Title Word Cloud",
    subtitle = "Colored by Sentiment
      Bluer for postive sentiments
      Yellower for negative sentiment"
  )
```

```{r non-election-wordcloud-data-prep, echo = FALSE, warning = FALSE}
# Isolating the title variable
no_election_title <- youtube %>%
  filter(election_years == 0) %>%
  select(title)

# Data Wrangling steps
docs <- VCorpus(VectorSource(no_election_title))
docs <- docs %>%
  # Removing numbers
  tm_map(removeNumbers) %>%
  # Removing punctuation
  tm_map(removePunctuation) %>%
  # Removing whitespace
  tm_map(stripWhitespace)

# transforming words to lowercase
docs <- tm_map(docs, content_transformer(tolower))
# removing words that contain brand names
docs <- tm_map(docs, removeWords, c(
  "super", "bowl", "commercial", "superbowl",
  "bud", "light", "budweiser", "pepsi",
  "hyundai", "doritos", "coke", "cocacola",
  "cola", "coca", "the", "kia","toyota"
))

# Creating df that can be used by ggwordcloud
dtm <- TermDocumentMatrix(docs)
matrix <- as.matrix(dtm)
words <- sort(rowSums(matrix), decreasing = TRUE)
non_election_df <- data.frame(word = names(words), freq = words)

# Adding the sentiment score variable
non_election_df <- non_election_df %>%
  mutate(angle = sample(-45:45, nrow(non_election_df), replace = TRUE)) %>%
  filter(freq >= 2) %>%
  mutate(sentiment = get_sentiment(word,"syuzhet"))
```


``` {r non-election-wordcloud-viz, out.width = "90%", fig.width = 10, fig.height = 8, echo = FALSE, warning = FALSE, cache = TRUE}
no_elec_wordC <- non_election_df %>%
  ggplot(aes(
    label = word,
    color = sentiment,
    size = freq,
    angle = angle
  )) +
  geom_text_wordcloud() +
  scale_radius(range = c(3.5, 15)) +
  theme_minimal() +
  scale_color_gradient(low = "#FFD662FF", high = "#00539CFF")+
  labs(
    title = "Non-election Year Ad Title Word Cloud")

library(patchwork)
elec_word_C / no_elec_wordC

```
]

---

``` {r election-col, echo = FALSE, warning = FALSE}
# Creating variable with election, using pivot_longer to get attributes in the
# same column, and creating a percentage variable
election_year <- c(2000, 2004, 2008, 2012, 2016, 2020)
# Adding an election year variable
youtube <- youtube %>%
  mutate(election_years = ifelse(year %in% election_year, 1, 0))
election_yr <- youtube %>%
  pivot_longer(cols = c(use_sex, funny, celebrity, patriotic, danger, animals)) %>%
  filter(election_years == 1) %>%
  filter(value == TRUE) %>%
  group_by(name) %>%
  summarise(n = n()) %>%
  mutate(perc = paste(round((n / sum(n)) * 100), "%", sep = ""))
```


### Content Comparision

.pull-left[
``` {r election-col-plot, out.width = "130%", fig.width = 15, fig.height = 20, echo = FALSE, warning = FALSE}
# Creating the plot
election_yr %>%
  ggplot(aes(y = name, x = n, fill = name)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = perc, color = name), nudge_x = 2, show.legend = FALSE,
            size = 8) +
  labs(
    x = "Count",
    y = "Ad Attribute",
    title = "Count and Proportion of Ad by Attribute",
    subtitle = "In Election Years"
  ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme_minimal()+
  theme(text = element_text(size = 25)) +
  scale_y_discrete(labels = rev(c("Use Sex",
                              "Patriotic",
                              "Funny",
                              "Danger",
                              "Celebrity",
                              "Animals")))
```
]

```{r non-election-col, echo = FALSE, warning = FALSE}
# Creating variable with no election, using pivot_longer to get attributes in the
# same column, and creating a percentage variable
no_election_yr <- youtube %>%
  pivot_longer(cols = c(use_sex, funny, celebrity, patriotic, danger, animals)) %>%
  filter(election_years == 0) %>%
  filter(value == TRUE) %>%
  group_by(name) %>%
  summarise(n = n()) %>%
  mutate(perc = paste(round((n / sum(n)) * 100), "%", sep = ""))
```

.pull-right[
```{r non-election-col-plot, out.width = "130%", fig.width = 15, fig.height = 20, echo = FALSE, warning = FALSE}
# No Election year col vizualization
no_election_yr %>%
  ggplot(aes(y = name, x = n, fill = name)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = perc, color = name), nudge_x = 4, show.legend = FALSE,
            size = 8) +
  labs(
    x = "Count",
    y = "Ad Attribute",
    title = "Count and Proportion of Ad by Attribute",
    subtitle = "In Non-Election Years"
  ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme_minimal() +
  theme(text = element_text(size = 25)) +
  scale_y_discrete(labels = rev(c("Use Sex",
                              "Patriotic",
                              "Funny",
                              "Danger",
                              "Celebrity",
                              "Animals")))

```
1. Marginal difference in Patriotic 
2. Change in Use Sex
]



